Utilizing Convolution for Obstacle Avoidance during Robotic Manipulator Movement

### 2023-07-27 Articles/ERK/erk.tex
ERK mid-joints

\begin{equation}
	\dot{q} = J^{\dagger}(q) \dot{x}_{ee} + N J^{\dagger}_{poi} \dot{x}_{poi}
	\label{eq:manipulator_kinematics}
\end{equation}

\todocomment{želena sredinska lega sklepov}

@@

An additional secondary task was also introduced, aimed at ensuring the manipulator's mid-joints remained in an upright position. This secondary task, aimed at maintaining the robot's "elbow" at the top, further reinforced the robot's upright posture while executing the primary task and the obstacle avoidance task.

>>>>

\begin{equation}
	\dot{q} = J^{\dagger}(q) \dot{x}_{ee} + N J^{\dagger}_{poi} \dot{x}_{poi} + N \dot{q}_{mid}
	\label{eq:manipulator_kinematics}
\end{equation}

We integrated a supplementary secondary task aiming to maintain the robot manipulator's joints as close to the midpoint of their range ( between $q(i)_{max}$ and $q(i)_{min}$ for the i-th joint ) as possible ( eq.~\ref{eq:mid-joints}). This auxiliary task, designed to elevate the robot's "elbow", reinforced the robot's upright posture during the execution of the primary task and the obstacle avoidance task.

\begin{equation}
	\dot{q}_{mid}(i) = w_m \left( \frac{q(i)_{max}-q(i)_{min}}{2} - q(i)\right) 
	\label{eq:mid-joints}
\end{equation}

@@
